A new breeding crossover approach for evolutionary algorithms

### 2023-09-21 paper.tex
General Updates

    In previous work, we introduced a population-based, bio-inspired algorithm\cite{Felix-Saul2022,Felix-Saul2023}. The proposed algorithm is inspired by the biological animal life cycle, consisting of the birth, growth, reproduction, and death stages\cite{read1968system}. Our algorithm was initially based on the canonical Genetic Algorithm (GA)\cite{holland1992genetic,holland1984genetic}, where all the individuals have a genotype (chromosome) constructed by a list of values, where we compute the individual's fitness using an evaluation function that represents the problem we wish to solve.

@@

    One essential feature to highlight in the algorithm is that it doesn't use the concept of generations in the evolution. Our strategy views the population as a set of candidate solutions that evolve continuously over time, which allows individuals of multiple ages to reproduce and generate new offspring, reflecting nature's actual behavior. Another difference to highlight in our algorithm is that both reproduction (crossover) and growth (mutation) execute through autonomous processes that interact with the population randomly. Figure~\ref{fig.algorithm_model} displays the general model concept for the Animal Life Cycle Algorithm (ALCA)\cite{Felix-Saul2023}.

>>>>

    In previous work, we introduced a population-based, bio-inspired algorithm\cite{Felix-Saul2022,Felix-Saul2023}. The proposed algorithm is inspired by the biological animal life cycle, consisting of the birth, growth, reproduction, and death stages\cite{read1968system}. Our algorithm was initially based on the canonical Genetic Algorithm (GA)\cite{holland1992genetic,holland1984genetic}, where the individual genotype design is defined by a set of values (chromosome). We compute each individual's fitness using a mathematical evaluation function representing the problem we wish to solve.

@@

    One essential feature to highlight in the algorithm is that it doesn't use the concept of generations in the evolution. Our strategy views the population as a set of candidate solutions that evolve continuously over time, which allows individuals of multiple ages to reproduce and generate new offspring, reflecting nature's actual behavior. Another difference to highlight in our algorithm is that both reproduction (crossover) and growth (mutation) execute through autonomous processes that interact with the population stochastically. Figure~\ref{fig.algorithm_model} displays the general model concept for the Animal Life Cycle Algorithm (ALCA)\cite{Felix-Saul2023}.
